---
title: "GuppyForagingPlasticity"
author: "Lauren E Johnson"
date: "9/20/2021"
output:
  pdf_document: default
  html_document: default
---

Importing the data 
```{r}
getwd()
setwd("C:/Users/laure/OneDrive/Documents/1.WUSTL/GordonLab/ForagingPlasticity/data/processed")

df <- read.csv("ForagingAssayData_2021_10_25_8.28.csv", stringsAsFactors = F)
```

Subsetting the data by **population** and **sex**
```{r}
df.ah <- df[which(df$Population == "AH"),]
df.ah.F <- df.ah[which(df.ah$Sex == "F"),]
df.ah.M <- df.ah[which(df.ah$Sex == "M"),]

df.al <- df[which(df$Population == "AL"),]
df.al.F <- df.al[which(df.al$Sex == "F"),]
df.al.M <- df.al[which(df.al$Sex == "M"),]


```


Summary of 4 df
```{r}
summary(df.ah.F)

summary(df.ah.M)

summary(df.al.F)

summary(df.al.M)

```



Create boxplots 
https://r-graphics.org/recipe-bar-graph-adjust-width
```{r}
library(ggplot2)

bx.ah.F <- ggplot(df.ah.F, aes(Pred_Tutor, Attempts, fill = Water)) 
  
bx.ah.F + geom_violin(alpha = 0.25, position = position_dodge(0.7)) + 
  geom_boxplot(width = 0.1, position = position_dodge(0.7)) + 
  #ylim(0,275) +
  mdthemes::md_theme_classic() + 
  labs(subtitle= "Aripo High Predation Females", x = NULL, y = "Foraging Attempts",color = "black") + 
  stat_summary(fun.y=mean, geom="point", color = "black", shape = 4, show.legend = F, position = position_dodge(0.7)) + 
  theme_classic()
```

```{r}
library(ggplot2)

bx.ah.M <- ggplot(df.ah.M, aes(Pred_Tutor, Attempts, fill = Water)) 
  
bx.ah.M + geom_violin(alpha = 0.25, position = position_dodge(0.7)) + 
  geom_boxplot(width = 0.1, position = position_dodge(0.7)) +
  #ylim(0,275) +
  mdthemes::md_theme_classic() + 
  labs(subtitle= "Aripo High Predation Males", x = NULL, y = "Foraging Attempts",color = "black") + 
  stat_summary(fun.y=mean, geom="point", color = "black", shape = 4, show.legend = F, position = position_dodge(0.7)) + 
  theme_classic()
```

Note to self: I'm not really digging how squished the violin and boxplots look on the AL male and female graphs
I understand standardizing the axis but I wonder if this can be a misleading visual display of the data?


```{r}
library(ggplot2)

bx.al.F <- ggplot(df.al.F, aes(Pred_Tutor, Attempts, fill = Water)) 
  
bx.al.F + geom_violin(alpha = 0.25, position = position_dodge(0.7)) + 
  geom_boxplot(width = 0.1, position = position_dodge(0.7)) + 
  #ylim(0,275) +
  mdthemes::md_theme_classic() + 
  labs(subtitle= "Aripo Low Predation Females", x = NULL, y = "Foraging Attempts",color = "black") + 
  stat_summary(fun.y=mean, geom="point", color = "black", shape = 4, show.legend = F, position = position_dodge(0.7)) + 
  theme_classic()
```

```{r}
library(ggplot2)

bx.al.M <- ggplot(df.al.M, aes(Pred_Tutor, Attempts, fill = Water)) 
  
bx.al.M + geom_violin(alpha = 0.25, position = position_dodge(0.7)) + 
  geom_boxplot(width = 0.1, position = position_dodge(0.7)) + 
  #ylim(0,275) +
  mdthemes::md_theme_classic() + 
  labs(subtitle= "Aripo Low Predation Males", x = NULL, y = "Foraging Attempts",color = "black") + 
  stat_summary(fun.y=mean, geom="point", color = "black", shape = 4, show.legend = F, position = position_dodge(0.7)) + 
  theme_classic()
```



Survival Plots
Palette from display.brewer.pal
Palette name "Pairs"
Light blue: "#A6CEE3"
Dark blue: "#1F78B4"
Light orange: "#FDBF6F"
Dark orange: "#FF7F00"

```{r}
library(ggpubr)
library(survminer)
library(survival)

fit.ah.F <- survfit(Surv(Latency) ~ Pred_Tutor, data = df.ah.F)

ggsurvplot(fit.ah.F, facet.by = "Water", data = df.ah.F, 
           palette = c("#A6CEE3", "#FDBF6F" , "#1F78B4","#FF7F00"), 
           ylab = "Proportion of fish that have not foraged", 
           title = "Aripo High Predation Females")

```

```{r}

fit.ah.M <- survfit(Surv(Latency) ~ Pred_Tutor, data = df.ah.M)

ggsurvplot(fit.ah.M, facet.by = "Water", data = df.ah.M, 
           palette = c("#A6CEE3", "#FDBF6F" , "#1F78B4","#FF7F00"), 
           ylab = "Proportion of fish that have not foraged", 
           title = "Aripo High Predation Males")

```

```{r}

fit.al.F <- survfit(Surv(Latency) ~ Pred_Tutor, data = df.al.F)

ggsurvplot(fit.al.F, facet.by = "Water", data = df.al.F, 
           palette = c("#A6CEE3", "#FDBF6F" , "#1F78B4","#FF7F00"), 
           ylab = "Proportion of fish that have not foraged", 
           title = "Aripo Low Predation Females")

```

```{r}

fit.al.M <- survfit(Surv(Latency) ~ Pred_Tutor, data = df.al.M)

ggsurvplot(fit.al.M, facet.by = "Water", data = df.al.M, 
           palette = c("#A6CEE3", "#FDBF6F" , "#1F78B4","#FF7F00"), 
           ylab = "Proportion of fish that have not foraged", 
           title = "Aripo Low Predation Males")

```



Statistical Analysis 


Statistics 
Mixed Effects Cox Regression
Used to model survival data when there are repeated measures of an individual 
Resource: https://stats.idre.ucla.edu/r/dae/mixed-effects-cox-regression/

```{r}

#install.packages("coxme")

library(coxme)


cox <- coxme(Surv(Latency) ~ Population + Sex + Pred * Tutor_pop * Water + (1 | ID), data = df)
summary(cox)

```
```{r}

cox <- coxme(Surv(Latency) ~ Population + Pred + Tutor_pop + Water + (1 | ID), data = df)
summary(cox)

```

```{r}

cox.ah.F <- coxme(Surv(Latency) ~ Pred * Tutor_pop * Water + (1 | ID), data = df.ah.F)
summary(cox.ah.F)
```

```{r}

cox.ah.M <- coxme(Surv(Latency) ~ Pred * Tutor_pop * Water + (1 | ID), data = df.ah.M)
summary(cox.ah.M)

```

```{r}

cox.al.F <- coxme(Surv(Latency) ~ Pred * Tutor_pop * Water + (1 | ID), data = df.al.F)
summary(cox.al.F)

```


```{r}

cox.al.M <- coxme(Surv(Latency) ~ Pred * Tutor_pop * Water + (1 | ID), data = df.al.M)
summary(cox.al.M)

```